---
title: "Weight of Fish"
author: "Daniel"
date: "Fall 2023"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
library(leaps)
library(dplyr)
fish <- read.csv(file="Fish.csv",header = TRUE)
```

# Predicting Fish Weight

Find the best model using two variables to predict perch weight and compare this to the best overall model.

## Perch
```{r}
perch = filter(fish, Species == "Perch")
```

### Best Two regressor model

```{r}
modelperch <- regsubsets(Weight ~  Length1 + Length2 + Length3 + Height + Width ,data=perch, nvmax = )
summary(modelperch)
```

### Best 2-varible prediction is

```{r}
best2perch = lm(Weight ~ Height+Width, data = perch)
summary(best2perch)
```

## Best 2-varible equation

Weight = -536 + 0.00112 * Height + 0.05309 * Width

### Best Models



## Pike

```{r}
pike = filter(fish, Species == "Pike")
```

### Best Two regressor model

```{r}
modelpike <- regsubsets(Weight ~  Length1 + Length2 + Length3 + Height + Width ,data=pike, nvmax = )
summary(modelpike)
```

### Best 2-varible prediction is

```{r}
best2pike = lm(Weight ~ Length1+Length3, data = pike)
summary(best2pike)
```

### Best 2-varible equation

Weight = -1675.79 + 0.04336 * Length1 +  0.00482 * Length3

### Best Models



## Roach

```{r}
Roach = filter(fish, Species == "Roach")
```

### Best Two regressor model

```{r}
modelRoach <- regsubsets(Weight ~  Length1 + Length2 + Length3 + Height + Width ,data=Roach, nvmax = )
summary(modelRoach)
```

### Best 2-varible prediction is

```{r}
best2Roach = lm(Weight ~ Length3+Width, data = Roach)
summary(best2Roach)
```

### Best 2-varible equation

Weight = -319.118 + 0.282 * Length3 + 0.115 * Width

### Best Models

## Final Summary Statements

The best model for perch prediction was -536 + 0.00112 * Height + 0.05309 * Width, for pike it was -1675.79 + 0.04336 * Length1 +  0.00482 * Length3, and for roach was Weight = -319.118 + 0.282 * Length3 + 0.115 * Width.
The best adjusted R-squares for each is, in descending order; Pike with 0.9649, Perch with 0.94, and Roach with 0.8482